Project 1 Checkpoint

### 2015-01-31 project1/checkpoint/main.tex
Stubbing out basic structure for paper
Adding the first draft of the problem description

HELLO WORLD \cite{pde_solution}
\bibliographystyle{plain}
\bibliography{main}

>>>>

\title{Project 1 Checkpoint}
\author{Chip Bell}
\date{February 6th, 2015}
\maketitle

\section{Problem Description}
Traffic simulation is becoming increasing important due to the expansion and growth of cities. Long-standing
infrastructure is forced to adapt in order to accomodate greater amounts of traffic, despite the fact that in many
cases the roads cannot be modified. This can be a result of legislation, existing buildings, and private property among
other things. So as a result, cities must instead optimize the variables they can control. In this case, we consider
signal light timing for the 12th St. and Peachtree Street intersection in only the north and south directions due to
time constraints, and the sheer difficulty with modeling traffic in general. In particular, we explore the effects that
light timing has on traffic flow, given a source input distribution of cars.

\section{The Conceptual Model}
Conceptual Model

\section{Simulation Software Architecture}
Simulation Software

\section{Current Build}
Current Build

\cite{pde_solution}
\bibliographystyle{plain}
\bibliography{main}
